### 2021-04-14 pldi21/intro.tex
cleanup spacing issues, add alt descriptions, misc cleanup

\begin{figure*}
  \begin{minipage}[t]{0.38\textwidth}
    \begin{subfigure}[t]{\linewidth}
    \begin{snugshade}
      \vspace*{-2mm}
      \caption{\textbf{Prior Work:} Graphite \cite{Graphite}}
       \label{fig:graphite}
      \vspace*{1mm}
     \end{snugshade}
      \vspace*{-1mm}
      \includegraphics[width=\linewidth]{graphite-color-palette-green.png}
      \vspace*{-5mm}
    \end{subfigure}
    \hspace{8mm}
    \begin{subfigure}[t]{\linewidth}
     \begin{snugshade}
      \vspace*{-2mm}
      \caption{\textbf{This Paper:} Livelits are live and compositional}
    \label{fig:color}
      \vspace*{1mm}
     \end{snugshade}
      \vspace*{-1mm}
      \includegraphics[width=\linewidth]{slider-color-livelits.png}
    \end{subfigure}
  \end{minipage}
  \hspace{10.5mm}
  \begin{subfigure}[t]{0.55\textwidth}
  \begin{snugshade}
   \vspace*{-2mm}
    \caption{\textbf{Case Study}: Grading with Livelits}
    \label{fig:grading}
    \vspace*{1mm}
     \end{snugshade}
    \vspace*{-1mm}
    \includegraphics[width=\linewidth]{grade-cutoff-livelit.png}
  \end{subfigure}
  \vspace{-5mm}
   \caption{Introductory Examples}
%   \vspace*{-2mm}
\end{figure*}

@@

\citet{Graphite} evaluated Graphite by surveying 473 developers
and \citet{DBLP:conf/uist/KeryRHMWP20} evaluated \textbf{mage} by interviewing 9 developers.
Both studies found that
participants viewed the proposed mechanism favorably and
would use a suitable GUI some or all of the time.
% \footnote{When presented with a color palette,
% many participants remarked that they rarely entered colors directly into Java code,
% but rather into stylesheets.
% Other palettes, e.g. a palette
% that supported regular expression construction, were viewed as more
% suitable for Java code.
% The mechanisms being considered are suitable both for general-purpose languages
% and typed domain-specific languages like typed stylesheets, which can often be embedded into modern
% general-purpose languages.}
This and other prior work also collectively showcase a wide variety of use cases \cite{Graphite,DBLP:conf/uist/KeryRHMWP20,interactive-visual-syntax},
and the Graphite survey solicited dozens of additional use cases from participants,
which the authors systematically taxonomize \cite{Graphite}.
We take these extensive empirical findings
as evidence for, and a showcase of,
the value of this broad class of mechanisms for integrating GUIs with code.
\vspace{-1mm}
\subsection{Contributions}
\label{sec:contributions}
We turn our attention in this paper to a number of fundamental technical
deficiencies that limit both GUI providers and clients using these prior mechanisms.
To address these,
we introduce a system of \emph{live literals}, or \emph{livelits},
demonstrated in Fig.~\ref{fig:color}.
Livelits are unique in achieving all of the following properties.
(Sec.~\ref{sec:related-work} describes which subset of these
are achieved by prior systems,
including those just mentioned.)

\newcommand{\llproperty}[1]{\vspace{5px}\noindent\textbf{#1}.}

>>>>

\begin{figure*}
  \begin{minipage}[t]{0.38\textwidth}
    \begin{subfigure}[t]{\linewidth}
    \begin{snugshade}
      \vspace*{-2mm}
      \caption{\textbf{Prior Work:} Graphite \cite{Graphite}}
       \label{fig:graphite}
      \vspace*{1mm}
     \end{snugshade}
      \vspace*{-1mm}
      \includegraphics[width=\linewidth]{graphite-color-palette-green.png}
      \Description{A reproduction of a Graphite color palette appearing as a pop above Java code where the cursor is in a hole of type \li{Color}.}
      \vspace*{-5mm}
    \end{subfigure}
    \hspace{8mm}
    \begin{subfigure}[t]{\linewidth}
     \begin{snugshade}
      \vspace*{-2mm}
      \caption{\textbf{This Paper:} Livelits are live and compositional}
    \label{fig:color}
      \vspace*{1mm}
     \end{snugshade}
      \vspace*{-1mm}
      \includegraphics[width=\linewidth]{slider-color-livelits.png}
      \Description{An application of the \li{\$color} livelit to compute a shade of green as described in the text.}
    \end{subfigure}
  \end{minipage}
  \hspace{10.5mm}
  \begin{subfigure}[t]{0.55\textwidth}
  \begin{snugshade}
   \vspace*{-2mm}
    \caption{\textbf{Case Study}: Grading with Livelits}
    \label{fig:grading}
    \vspace*{1mm}
     \end{snugshade}
    \vspace*{-1mm}
    \includegraphics[width=\linewidth]{grade-cutoff-livelit.png}
    \Description{A case study involving several livelits which are described in the text.}
  \end{subfigure}
  \vspace{-5mm}
   \caption{Introductory Examples}
%   \vspace*{-2mm}
\end{figure*}

@@

\citet{Graphite} evaluated Graphite by surveying 473 developers
and \citet{DBLP:conf/uist/KeryRHMWP20} evaluated \textbf{mage} by interviewing 9 developers.
Both studies found that
participants viewed the proposed mechanism favorably and
would use a suitable GUI some or all of the time.
% \footnote{When presented with a color palette,
% many participants remarked that they rarely entered colors directly into Java code,
% but rather into stylesheets.
% Other palettes, e.g. a palette
% that supported regular expression construction, were viewed as more
% suitable for Java code.
% The mechanisms being considered are suitable both for general-purpose languages
% and typed domain-specific languages like typed stylesheets, which can often be embedded into modern
% general-purpose languages.}
This and other prior work also collectively showcase a wide variety of use cases \cite{Graphite,DBLP:conf/uist/KeryRHMWP20,interactive-visual-syntax},
and the Graphite survey solicited dozens of additional use cases from participants,
which the authors systematically taxonomize \cite{Graphite}.
We take these extensive empirical findings
as evidence for, and a showcase of,
the value of this broad class of mechanisms for integrating GUIs with code.
\subsection{Contributions}
\label{sec:contributions}
We turn our attention in this paper to a number of fundamental technical
deficiencies that limit both GUI providers and clients using these prior mechanisms.
To address these,
we introduce a system of \emph{live literals}, or \emph{livelits},
demonstrated in Fig.~\ref{fig:color}.
Livelits are unique in achieving all of the following properties.
(Sec.~\ref{sec:related-work} describes which subset of these
are achieved by prior systems,
including those just mentioned.)

\newcommand{\llproperty}[1]{\vspace{5px plus 5px minus 3px}\noindent\textbf{#1}.}
